### 2016-09-01 paper.tex
Revert "Change title to include 'hydrokinetic'"
This reverts commit bc6d3ad89099eb0c5cd352ab24e956631c6486bc.

{\Large \textbf\newline{Experimental Study of a Reference Model
        Cross-Flow Hydrokinetic Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

    \caption{{\bf Turbine Model.} A drawing of the turbine model.}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-perf_re_dep.eps}

>>>>

{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
        Cross-Flow Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

    \caption{{\bf Turbine Model.} A drawing of the RM2 turbine model. All
    dimensions are in meters}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-perf_re_dep.eps}
